---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

#### Add a project state badge 

```{r, echo=FALSE, results='asis'}
bcgovr::devex_badge("Exploration")
```

# Summary of Provincial Grizzly Bear informaiton for an Area of Interet for Integrated Monitoring reporting

### Usage

There are six core scripts that are required for the analysis, the run_all.R script sets the enviornment variables:

- run_all_AOI.R - Area of Interest information entered in run script
- 01_load.R
- 02_clean.R
- 03_analysis_Maps.R
- 03_analysis_BoxPlots.R - which calls boxplotsGB.R and BoxGB.R
- 03_analysis_GBPU_Rank.R


### Project Status
This project is under active development.

### Getting Help or Reporting an Issue

To report bugs/issues/feature requests, please file an [issue](https://github.com/bcgov/IM-Report-GBears/issues).

### How to Contribute

If you would like to contribute, please see our [CONTRIBUTING](CONTRIBUTING.md) guidelines.

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.

### License

    Copyright 2017 Province of British Columbia

    Licensed under the Apache License, Version 2.0 (the "License");
    you may not use this file except in compliance with the License.
    You may obtain a copy of the License at 

       http://www.apache.org/licenses/LICENSE-2.0

    Unless required by applicable law or agreed to in writing, software
    distributed under the License is distributed on an "AS IS" BASIS,
    WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
    See the License for the specific language governing permissions and
    limitations under the License.
    
This repository is maintained by [ENVEcosystems](https://github.com/orgs/bcgov/teams/envecosystems/members).    

